HO unification from object language to meta language

### 2024-03-28 paper/main.tex

\begin{gather}
\lambda x y.F \appsep y \appsep x = \lambda x y.x \label{eq:unif-eta1}\\
\lambda x. f \appsep (F \appsep x) \appsep x = f \appsep (\lambda y.y) \label{eq:unif-eta2}
\end{gather}
Note that here $F$ is used with different arities, moreover
in the second problem the left hand side happens to be an
eta expansion (of $f (\lambda y.y)$) only after we discover that
$F = \lambda x\lambda y.y$ (i.e. that $F$ discards the $x$ argument).
Both problems are addressed in the next section.

>>>>

\begin{gather}
\lambda x y.F \appsep y \appsep x = \lambda x y.x \label{eq:unif-eta1}\\
\lambda x. f \appsep (F \appsep x) \appsep x = f \appsep (\lambda y.y) \label{eq:unif-eta2}
\end{gather}
Note that here $F$ is used with different arities, moreover
in the second problem the left hand side happens to be an
eta expansion (of $f (\lambda y.y)$) only after we discover (at run time)
that $F = \lambda x\lambda y.y$ (i.e. that $F$ discards the $x$ argument).
Both problems are addressed in the next section.
